Simple Type Theory is not too Simple

### 2021-03-30 article.tex
Update acknowledgments
Added the snippet for lemma isomorphic_to_local_is_local

@@

Work on this paper was supported by the European Research Council Advanced Grant ALEXANDRIA (Project 742178).

>>>>

\begin{isabelle}
\isacommand{lemma}\isamarkupfalse%
\ isomorphic{\isacharunderscore}{\kern0pt}to{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}local{\isacharcolon}{\kern0pt}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}local{\isacharunderscore}{\kern0pt}ring\ B\ addB\ multB\ zeroB\ oneB{\isachardoublequoteclose}\isanewline
\ \ \ \ \isakeyword{and}\ {\isachardoublequoteopen}ring{\isacharunderscore}{\kern0pt}isomorphism\ f\ A\ addA\ multA\ zeroA\ oneA\ B\ addB\ multB\ zeroB\ oneB{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}local{\isacharunderscore}{\kern0pt}ring\ A\ addA\ multA\ zeroA\ oneA{\isachardoublequoteclose}
\end{isabelle}

@@

Work on this paper was supported by the ERC Advanced Grant ALEXANDRIA (Project GA 742178).
